\documentclass{book}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\usepackage{hyperref}%
\usepackage{titlesec}%
\titleformat{\chapter}[display]%
{\normalfont\bfseries}{}{0pt}{\Huge}%
\title{Maia's Songbook}%
\author{Maia McCormick}%
\date{\today}%
%
\begin{document}%
\normalsize%
\pagenumbering{gobble}%
\maketitle%
\tableofcontents%
\pagenumbering{arabic}%
\chapter{Let Union Be in All Our Hearts}%
\label{letunionbeinallourhearts}%
By %
\textit{trad.}%
\newline%
Come my lads and let's be jolly\newline%
Drive away dull melancholy,\newline%
For to grieve it would be folly\newline%
While we are together.\newline%
\newline%
(Chorus)\newline%
Let union be in all our hearts,\newline%
Let all our hearts be joined as one.\newline%
We'll end the day as we began,\newline%
We'll end it all in pleasure.\newline%
Whack{-}folla{-}rolla{-}rye, too{-}ra{-}lie{-}doe (3x)\newline%
While we are together.\newline%
\newline%
Old King Solomon in all his glory\newline%
Told each wife a different story:\newline%
In our cups we'll sing him glory\newline%
While we are together.\newline%
\newline%
Eating and drinking there's a charm in,\newline%
Smoking and piping there's no harm in.\newline%
All these things we'll take delight in\newline%
While we are together.\newline%
\newline%
Grab the bottle as it passes,\newline%
Do not fail to fill your glasses.\newline%
Water drinkers are dull asses\newline%
While we are together.\newline%
\newline%
Cease your quarreling and your fighting,\newline%
Evil{-}speaking and backbiting.\newline%
All these things take no delight in\newline%
While we are together.\newline%
%
\chapter{John Ball}%
\label{johnball}%
By %
\textit{Sydney Carter}%
\newline%
Who’ll be the lady,\newline%
Who will be the lord,\newline%
When we are ruled by the love of another?\newline%
(Repeat)\newline%
\newline%
CHORUS:\newline%
Sing, John Ball, and tell it to them all {-}\newline%
Long live the day that is dawning!\newline%
For I'll crow like a cock,\newline%
I'll carol like a lark,\newline%
For the light that is coming in the morning.\newline%
\newline%
Eve is the lady, Adam is the lord,\newline%
When we are ruled by the love of another...\newline%
(Repeat)\newline%
\newline%
Labor and spin for fellowship, I say,\newline%
Labor and spin for the love of one another...\newline%
(Repeat)\newline%
\newline%
All will be ruled by fellowship, I say,\newline%
When we are ruled by the love of one another...\newline%
(Repeat)\newline%
\newline%
%
\chapter{Indexes}%
\section{Traditional}%
\hyperref[letunionbeinallourhearts]{Let Union Be in All Our Hearts}%
\hyperref[johnball]{John Ball}

%
\section{Uptempo}%
\hyperref[johnball]{John Ball}

%
\end{document}